---
title: "QMM_11"
author: "sai prasad desineni/811191807"
date: '2022-11-21'
output: pdf_document
---

```{r}
#loading libraries 
library(lpSolveAPI)

#loading the dataset
ipmodel = read.lp("C:/Users/desineni/Downloads/AP.lp")
ipmodel

```
```{r}
solve(ipmodel)
#the value obtained "0" shows that he model exists

```


```{r}
get.objective(ipmodel)
### therefore the total wages while ensuring that there are sufficient number of workers available
### each day is 25675$
```


```{r}
get.variables(ipmodel)
```
x1 = Employees on shit 1 = 2


x2 = Employees on shit 2 = 4


x3 = Employees on shit 3 = 5


x4 = Employees on shit 4 = 0


x5 = Employees on shit 5 = 8


x6 = Employees on shit 6 = 1


x7 = Employees on shit 7 = 13


the number of workers available each day are 


sunday = x2 + x3 + x4 + x5 + x6 = 18
\newline
monday = x3 + x4 + x5 + x6 + x7 = 27
\newline
tuesday = x4 + x5 + x6 + x7 + x1 = 24
\newline
wednesday = x5 + x6 + x7 + x1 + x2 = 26
\newline
Wednesday: x5 + x6 + x7 + x1 + x2 = 28
\newline
Thursday: x6 + x7 + x1 + x2 + x3 = 25
\newline
Friday: x7 + x1 + x2 + x3 + x4 = 24
\newline
Saturday: x1 + x2 + x3 + x4 + x5 = 19
\newline
```{r}
```


